### 2019-03-26 _publications/jors/paper.tex
Update abstract with @amjokisaari changes
Tried to incorporate @amjokosaari changes, but also keep the abstract
at ~100 words, which is a hard requirement from the journal. The new
abstract is ~110 words. The @amjokosaari version of the abstract was
~130 words, which is probably too many.

An online portal provides a valuable space for scientific communities
to summarize a shared challenge, collect attempts at a solution, and
present a quantitative comparison of past attempts in a compelling
way. An exemplar of such a portal is
$\mu$MAG~\cite{mumag}. The reusable PFHub
framework leverages existing online services to build a static portal
website that is considerably easier to deploy and maintain without
sacrificing content or scope. The first deployment of the PFHub
framework supports phase-field practitioners and code developers
participating in an effort to improve quality assurance for
phase-field codes.

%% ~\footnote{Certain commercial equipment,
%%   instruments, or materials (or suppliers, or software, ...) are
%%   identified in this paper to foster understanding. Such
%%   identification does not imply recommendation or endorsement by the
%%   National Institute of Standards and Technology, nor does it imply
%%   that the materials or equipment identified are necessarily the best
%%   available for the purpose.\label{disclaimer}}

%% ~\textsuperscript{\ref{disclaimer}}

>>>>

Scientific communities struggle with the challenge of effectively and
efficiently sharing content and data. An online portal provides a
valuable space for scientific communities to discuss challenges and
collate scientific results. Examples of such portals include the
Micromagenetic Modeling Group ($\mu$MAG~\cite{mumag}), the Iteratomic
Potentials Repository (IPR~\cite{}) and on a larger scale the NIH
Genetic Sequence Database (GenBank~\cite{}). In this work, we present
a description of a generic web portal that leverages existing online
services to provide a framework that may be adopted by other
scientific communities. The first deployment of the PFHub framework
supports phase-field practitioners and code developers participating
in an effort to improve quality assurance for phase-field codes.
